Using traffic analysis to identify The Second Generation Onion Router

### 2011-05-15 thesis/experiment.tex
Explain the attributes examined by netAI

The data captured was in the form of 1MB capture files which were recombined
with mergecap and processed by NetAI to produce ARFF format files for use by
Weka. Each data set were given the nominal classification 'http',
'http\_over\_tor' and 'https\_over\_tor', all other nominal attributes were
removed.

>>>>

The data captured was in the form of 1MB capture files which were recombined
with mergecap and processed by NetAI to produce ARFF format files for use by
Weka. NetAI identifies flows inside the capture files and produces a number
of statistics to be used as attributes for classification. The attributes
produced by NetAI are shown in table \ref{table:netmate-attributes}.

\begin{table}[H]
  \begin{tabular}{lll}
    \toprule
    Attribute name & Description \\
    \midrule
    srcip & Source IP address \\
    srcport & Source port \\
    dstip & Destination IP address \\
    dstport & Destination port \\
    proto & Protocol (TCP, UDP) \\
    total\_fpackets & Total forward packets \\
    total\_fvolume & Total forward volume \\
    total\_bpackets & Total backward packets \\
    total\_bvolume & Total backward volume \\
    min\_fpktl & Minimum forward packet length \\
    mean\_fpktl & Mean forward packet length \\
    max\_fpktl & Maximum forward packet length \\
    std\_fpktl & Std. Deviation of forward packet length \\
    min\_bpktl & Minmum backward packet length \\
    mean\_bpktl & Mean backward packet length \\
    max\_bpktl & Maximum backward packet length \\
    std\_bpktl & Std. Deviation of backward packet length \\
    min\_fiat & Minimum forward inter arrival time \\
    mean\_fiat & Mean forward inter arrival time \\
    max\_fiat & Maximum forward inter arrival time \\
    std\_fiat & Std. Deviation of forward inter arrival time \\
    min\_biat & Minimum backward inter arrival time \\
    mean\_biat & Mean backward inter arrival time \\
    max\_biat & Maximum backward inter arrival time \\
    std\_biat & Std. Devation of backward inter arrival time \\
    duration & Session duration \\
    min\_active & Minimum active \\
    mean\_active & Mean active \\
    max\_active & Maximum active \\
    std\_active & Std. Deviation active \\
    min\_idle & Minimum idle \\
    mean\_idle & Mean idle \\
    max\_idle & Maximum idle \\
    std\_idle & Std. Deviation of idle \\
    sflow\_fpackets & Sub flow forward packets \\
    sflow\_fbytes & Sub flow forward bytes \\
    sflow\_bpackets & Sub flow backward packets \\
    sflow\_bbytes & Sub flow backward bytes \\
    fpsh\_cnt & Forward push counter \\
    bpsh\_cnt & Backward push counter \\
    furg\_cnt & Forward urgent counter \\
    burg\_cnt & Backward urgent counter \\
    total\_fhlen & Total forward header length \\
    total\_bhlen & Total backward header length \\
    \bottomrule
    \label{table:netmate-attributes}
  \end{tabular}
  \caption{Captured Data}
\end{table}

Each data set was given the nominal classification 'http',
'http\_over\_tor' and 'https\_over\_tor', this attribute was appended as the
last attribute in the ARFF file.

This file was imported into the Weka program, all nominal attributes other than
the classification were removed and a number of classification algorithms were
trialled. The results of classification with all forty attributes is shown in
table \ref{table:results}.
